Brownian Dynein Model

### 2015-10-29 latex/derivation.tex
Revert to Ln/Lf unambiguous model.

\allowdisplaybreaks

@@

%% \begin{figure}[h!]
%%   \caption{Key lengths and angles in bothbound dynein model.}
%%   \centering
%%     \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
%% \end{figure}

\section{Derivation of bothbound tail coordinates}

\begin{align*}
  \theta_1 &= \cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right)\\
  \theta_2 &= \cos^{-1}\left(\frac{L}{2L_t}\right)\\
  L &= \sqrt{(X_{fm}-X_{nm})^2+(Y_{fm}-Y_{nm})^2}\\
\end{align*}

\subsection{$X_t$}
\begin{align*}
  X_t &= X_{nm} + L_t\cos(\theta_1 \pm \theta_2)\\
  &= X_{nm} + L_t\cos\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \cos\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}\\
  &= X_{nm} + L_t\left(\frac{X_{fm}-X_{nm}}{2L_t} \mp \sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{1 - \frac{L^2}{4L_t^2}}\right)\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2L}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{(Y_{fm}-Y_{nm})^2}\sqrt{\frac{4L_t}{L^2} - 1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} -1}\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))(L_s\cos(\theta_{nb})) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\mp \frac{d}{dt} \left(\frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{d}{dt} \left(\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\right)\\
   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{1}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right) *\\
   &\left(\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right) *\\
   &\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)\\
   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{\left(\frac{-4L_t^2\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right)\\
\end{align*}

\subsection{$Y_t$}
\begin{align*}
  Y_t &= Y_{nm} + L_t\sin(\theta_1 \pm \theta_2)\\
  &= Y_{nm} + L_t\sin\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}\\
  &= Y_{nm} + L_t\left(\frac{L}{2L_t}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{L}\sqrt{1 - \frac{L^2}{4L^2_t}}\right)\\
  &= Y_{nm} + \frac{L}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{2L}\sqrt{4L_t^2 - L^2}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{L^2} - 1}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{\left(Y_{fm}-Y_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} - 1}\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
\end{align*}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the bothbound Dynein model.\\
\begin{align}
  X_{nb} &= 0\\
  X_{nm} &= L_s\cos(\theta_{nb})\\
  X_{t}  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  X_{fm} &= B + L_s\cos(\theta_{fb})\\
  X_{fb} &= B \\
\end{align}

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &= L_s\sin(\theta_{nb})\\
  Y_{t}  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
  Y_{fm} &= L_s\sin(\theta_{fb})\\
  Y_{fb} &= 0\\
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb}\\
  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + -L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  &\pm \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2} \left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb}\\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                  
  \dot{Y}_{nb} &= 0 \\                                 
  \dot{Y}_{nm} &= L_s\cos(\theta_{nb})\dot{\theta}_{nb}\\
  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\pm \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1} \\
 &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}-BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\
  \dot{Y}_{fm} &= L_s\cos(\theta_{fb})\dot{\theta}_{fb}\\
  \dot{Y}_{fb} &= 0 \\
\end{align}

>>>>

@@

\begin{figure}[h!]
  \caption{Key lengths and angles in bothbound dynein model.}
  \centering
    \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
\end{figure}

\section{Cartesian Coordinate Derivation}

By the law of cosines:
\begin{align}
  L_n &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})}\\
  L_f &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})}\\
\end{align}

We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\

Also by the law of cosines, we see that:
\begin{align}
  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
\end{align}

We use these equations to solve for our nm (near motor) coordinates:

\begin{align}
  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
\end{align}

We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)\pm
cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}$$
and $$\sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}$$ to simplify our expressions:

\begin{align}
  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
\end{align}

We simplify further...

\begin{align}
  X_{nm} &= \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
\end{align}

\begin{align}
  X_{nm} &= \frac{1}{4LL_s}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big)\big(L_n \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
\end{align}

Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.

\begin{align}
  \dot{X}_{nm} =
  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
   \text{Ln}(t)^2}\right)}{2
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
   \text{Ln}(t)^2}}} - \\
  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
   \text{Ln}(t)^3}\\
  &-\frac{\text{Ls}
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
       \text{Ln}(t)^2}}}\\
  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
   \text{Ln}(t)^2}
\end{align}

We can also use the law of cosines to find an expression for $\Theta_{1}$:

\begin{align}
   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
\end{align}

We use this to find the value of $X_{t}$:

\begin{align}
  X_{t} &= L_n\cos(\Theta_{1}) \\
       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
\end{align}

To find $Y_{t}$ we do something similar:

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &=  \\
  X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
  X_{fm} &=  \\
  X_{fb} &= L \\
\end{align}

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &=  \\
  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
  Y_{fm} &=  \\
  Y_{fb} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= \\
  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
  \dot{X}_{fm} &= \\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{nb} &= 0 \\                                         
  \dot{Y}_{nm} &= \\
  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
  \dot{Y}_{fm} &= \\
  \dot{Y}_{fb} &= 0 \\
\end{align}
